Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-18 ch04-lrmhinf/lrmhinf.tex
Add section to link robust control and peak model

In robust control~\citep{Zhou1996,Skogestad2005}, the design is carried out while taking uncertainties into account.
This is typically done by considering that the actual plant $\true{\Plant} \in \ModelSet[]$.
Hence, the problem is then to construct the model set $\ModelSet[]$ as illustrated in \figref{fig:lrmhinf:modelset}.
The design process thus guarantees performance and stability for the whole set instead of for a single model.
However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model uncertainty $\Delta(\estimated{\Plant}, \true{\Plant})$.
A generic way to express the plant model set (see also \figref{fig:lrmhinf:modelset}) is
\begin{equation}
  \ModelSet[]_{\mathrm{generic}} 
  \isdef 
  \Set{ \Plant | \norm{\Delta(\estimated{\Plant}, \Plant)} \leq \gamma}
  \equiv
  \Set{ \Plant(\estimated{\Plant}, \Delta) | \norm{\Delta} \leq \gamma}
  \label{eq:lrmhinf:model-set:generic}
\end{equation}
where both the norm and the concrete function $\Delta(\estimated{\Plant}, \Plant)$ are a choice for the control engineer.
An example of such a model set is easily imagined for additive uncertainty ($\Plant(\estimated{\Plant}, \Delta) = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
\begin{equation}
  \ModelSet[]_{\mathrm{additive,2}} = \Set{ \Plant | \norm[2]{\estimated{\Plant} - \Plant} \leq \gamma}
  \text{,}
\end{equation}
which is a multidimensional ball with radius $\gamma$.
Note that in many cases, the uncertainty structure (additive, multiplicative, \ldots) can be converted to other representations~\citep{Douma2005}.

>>>>

In robust control~\citep{Zhou1996,Skogestad2005}, the design is carried out while taking uncertainties into account.
This is typically done by considering that the actual plant $\true{\Plant} \in \ModelSet[]$.
Hence, the problem is then to construct the model set $\ModelSet[]$ as illustrated in \figref{fig:lrmhinf:modelset}.
The design process thus guarantees performance and stability for the whole set instead of for a single model.
However, these guarantees hinge on proper specification of $\ModelSet[]$ which is typically done by estimating a nominal model $\estimated{\Plant}$ and the model error $\Delta(\estimated{\Plant}, \true{\Plant})$.
A generic way to express the plant model set (see also \figref{fig:lrmhinf:modelset}) is
\begin{equation}
  \ModelSet[]_{\mathrm{generic}} 
  \isdef 
  \Set{ \Plant | \norm{\Delta(\estimated{\Plant}, \Plant)} \leq \gamma}
  \label{eq:lrmhinf:model-set:generic}
\end{equation}
where both the norm and the exact uncertainty description $\Delta(\estimated{\Plant}, \Plant)$, can be chosen by the control engineer.
An example of such a model set is easily imagined for additive uncertainty ($\Plant = \estimated{\Plant} + \Delta$) when a $\Hardy_{2}$ norm is used, in that case one obtains
\begin{equation}
  \ModelSet[]_{\mathrm{additive,2}} 
  = 
  \Set{ \Plant | \Bignorm[2]{ \ezbrace{\Plant - \estimated{\Plant}}{\Delta(\estimated{\Plant}, \Plant)}  } \leq \gamma}
  \equiv
  \Set{  \ezbrace{\estimated{\Plant}  + \Delta}{\Plant(\estimated{\Plant}, \Delta)}  | \norm[2]{\Delta} \leq \gamma}
  \text{,}
\end{equation}
which is a multidimensional ball with radius $\gamma$ centered around $\estimated{\Plant}$.
Note that in many cases, the uncertainty structure (additive, multiplicative, \ldots) can be converted to other representations~\citep{Douma2005}.
